---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# blotr: Blotting matrices since 2016

This package does one thing: create symmetric matrices from asymmetric matrices.
It is inspired by [This
tweet](https://twitter.com/algaebarnacle/status/713103252582064128).

The basic idea is that you fold your matrix across the diagonal to create a 
symmetric matrix like an inkblot for a [Rorschach
test](https://en.wikipedia.org/wiki/Rorschach_test).

## How do I use it?

There is only one function called `blot()`.

### Simple example

```{r}
library("blotr")
set.seed(20160325)
mat <- matrix(sample(c(NA, 1), 100, replace = TRUE), 10, 10)
diag(mat) <- 0
mat
isSymmetric(mat)
```

The matrix is non-symmetrical! We'll make it symmetrical with `blot()`!

```{r}
blot(mat)
isSymmetric(blot(mat))
```

We can also choose to keep only the upper triangle if we wish:

```{r}
blot(mat, ut = TRUE)
```

### Now let's have some fun

Let's generate some inkblots and visualize them:

```{r}
set.seed(20160326)
mat <- matrix(NA_integer_, 100, 100)
x   <- replicate(10, rnorm(250, mean = sample((3:7)*10, 1), 5))
y   <- replicate(10, rnorm(250, mean = sample((3:7)*10, 1), 5))
obs <- matrix(round(c(x, y)), ncol = 2)
mat[obs]  <- 1L
diag(mat) <- 0L
isSymmetric(mat)
```

Now for the plotting. First, the without blotting:

```{r}
robs  <- range(obs)/100
fx    <- seq(0, 1, length.out = 100)
omar  <- par("mar")
par(mar = c(0, 0, 0, 0))
plot(NA, xlim = robs, ylim = robs, type = "n", asp = 1, ann = FALSE, axes = FALSE)
.filled.contour(fx, fx, mat, c(0, 1), col = "black")
par(mar = omar)
```

Now, with blotting:

```{r}
par(mar = c(0, 0, 0, 0))
plot(NA, xlim = robs, ylim = robs, type = "n", asp = 1, ann = FALSE, axes = FALSE)
.filled.contour(fx, fx, blot(mat), c(0, 1), col = "black")
par(mar = omar)
```


## Installation

You can install blotr via devtools::

```{r, eval = FALSE}
devtools::install_github("zkamvar/blotr")
```

