---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# blotmat: Blotting matrices since 2016

This package does one thing: create symmetric matrices from asymmetric matrices.
It is inspired by [This
tweet](https://twitter.com/algaebarnacle/status/713103252582064128).

The basic idea is that you fold your matrix across the diagonal to create a 
symmetric matrix like an inkblot for a [Rorschach
test](https://en.wikipedia.org/wiki/Rorschach_test).

## How do I use it?

There is only one function called `blot()`:

```{r}
library("blotmat")
set.seed(20160325)
mat <- matrix(sample(c(NA, 1), 100, replace = TRUE), 10, 10)
diag(mat) <- 0
mat
isSymmetric(mat)
blot(mat)
isSymmetric(blot(mat))
```

## Installation

You can install blotmat via devtools::

```{r, eval = FALSE}
devtools::install_github("zkamvar/blotmat")
```

